Manuscript

### 2022-02-03 analysis/manuscript.Rmd
wflow_publish("analysis/manuscript.Rmd")

paths_summary <- data %>% dplyr::select(exposure_description, outcome_description, gam_beta, rho_beta, omega_beta, gam_rho_resid, gam_vs_rho_BF_sig, omega_vs_rho_BF_sig, omega_vs_gam_BF_sig)

>>>>

paths_summary <- data %>% dplyr::select(exposure_description, outcome_description, gam_beta, rho_beta, omega_beta, gam_rho_resid, gam_vs_rho_pval, omega_vs_rho_pval, omega_vs_gam_pval)
